GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-09-16 paper/kbanotebook2013/paper.tex
added the bibliography structure
changed the author format so it compiles with pdflatex

\numberofauthors{3}

\author {

\alignauthor Morteza Shahriari\\
  \affaddr{University of Florida}\\
       \affaddr{Department of Computer \& Information Science \& Engineering}\\
       \affaddr{Gainesville, Florida, USA}\\
       \email{\{m.shahriarinia@ufl.edu}

\alignauthor Christan Grant, Yang Peng, Daisy Zhe Wang\\
  \affaddr{University of Florida}\\
       \affaddr{Department of Computer \& Information Science \& Engineering}\\
       \affaddr{Gainesville, Florida, USA}\\
       \email{\{cgrant,ypeng,daisyw\}@cise.ufl.edu}

\alignauthor Milenko Petrovic\\
  \affaddr{Institute for Human and Machine Cognition}\\
       %\affaddr{Department of Computer \& Information Science \& Engineering}\\
       \affaddr{Ocala, Florida, USA}\\
       \email{mpetrovic@ihmc.us}
}

@@

>>>>

%\numberofauthors{3}

\author {%
  Morteza Shahriari\\
  University of Florida\\
  Department of Computer \& Information Science \& Engineering\\
  Gainesville, Florida, USA\\
       {m.shahriarinia@ufl.edu}
\and
  Christan Grant, Yang Peng, Daisy Zhe Wang\\
  University of Florida\\
       Department of Computer \& Information Science \& Engineering\\
       Gainesville, Florida, USA\\
       {\{cgrant,ypeng,daisyw\}@cise.ufl.edu}
\and
  Milenko Petrovic\\
  Institute for Human and Machine Cognition\\
       %\affaddr{Department of Computer \& Information Science \& Engineering}\\
       Ocala, Florida, USA\\
       {mpetrovic@ihmc.us}
}

@@

\bibliographystyle{acm}
\bibliographystyle{citation}
